---
title: "Stickers_EF"
output:
html_notebook:
code_folding: hide
highlight: tango
theme: default
toc: yes
toc_depth: 5
toc_float: yes
date: '`r format(Sys.time(), "%B %d, %Y")`'
---

## Install packages

```{r, echo=FALSE}
packages <- c("tidyverse", "lme4", "multcomp", "effects", "optimx", "Rmisc", "lsmeans", "stringi", "car", "knitr", "sjPlot")
packages_new <- packages[!(packages %in% installed.packages()[,"Package"])]
if(length(packages_new)) install.packages(packages_new)
lapply(packages,library,character.only=T)

# set palette color for figures
palette(c("#84a59d", "#f6bd60"))

```


## Import data

```{r}

# read paper data
paper_data_path <- getwd()
df <- read.csv(paste0(paper_data_path, "/Study1_paper.csv"), header = TRUE, na.strings = c("."), quote='"', strip.white = TRUE)

df.csv_update <- read.csv(paste0(paper_data_path, "/Study1_DayNight.csv"), header = TRUE, na.strings = c(".", "NA"), quote='"', strip.white = TRUE)

```

## Reshape and recode

```{r message=FALSE, warning=FALSE}

## DAY-NIGHT TASK

# make sure variables are of the proper class
df.csv.new <- df.csv_update %>% group_by(participant) %>%
  dplyr::summarise(DN_total = sum(resp_key_image.corr)) %>%
  ungroup() %>%
  dplyr::rename(Participant = participant)

df.csv.new$Participant <- as.factor(sprintf("%03d", as.numeric(df.csv.new$Participant)))

## DATA SHEETS

# make sure variables are of the proper class
df$Participant <- as.factor(sprintf("%03d", as.numeric(df$Participant)))

# create new column for total stickers won
a <- dplyr::select(df, matches("win")) == 'Y'
df$Stickers_total <- sapply(df[,1], function(x) sum(as.integer(a[x,1:4]), na.rm=TRUE))
df$Stickers_prop <- df$Stickers_total / 4

df$Stickers_total_1sthalf <- sapply(df[,1], function(x) sum(as.integer(a[x,1:2]), na.rm=TRUE))
df$Stickers_total_2ndhalf <- sapply(df[,1], function(x) sum(as.integer(a[x,3:4]), na.rm=TRUE))

# change age to years
df$Age_in_years <- df$Age_in_days / 365
df$Age_cat <- NA
df$Age_cat[which(df$Age_in_years < 4.5)] <- "younger"
df$Age_cat[which(df$Age_in_years > 4.5)] <- "older"
df$Age_cat <- as.factor(df$Age_cat)

# only keep successes and add Day-Night computer task results to the dataframe
df_S <- subset(df, Success == 'S') %>%
  left_join(df.csv.new, by="Participant") 

df_S$Participant <- as.factor(df_S$Participant)
df_S$DN_prop <- df_S$DN_total / 16

# turn to long format
df.long <- df_S %>% gather("Time", "Sticker_win", Stickers_T1_win:Stickers_T4_win)
df.long$Time <- as.factor(sapply(df.long$Time, function(x) stri_replace_all_regex(x, '.(?<letters>[a-z|A-Z]+).', '')))
df.long$Time <- ordered(df.long$Time, levels = c("T1", "T2", "T3", "T4"))

df.long.pos <- df_S %>% gather("Time", "Sticker_location", Stickers_T1_location:Stickers_T4_location) %>%
  dplyr::select("Sticker_location")

df.long <- df.long %>% bind_cols(df.long.pos) %>%
  dplyr::select(-c(Stickers_T1_location:Stickers_T4_location))

df.long$Sticker_win <- as.factor(df.long$Sticker_win)

```

## Age demographics

```{r}

t.test(Age_in_years ~ Condition, data=df_S)

```

## Analyses

### DV: Stickers

#### Stickers by Condition, Age, and Gender

##### Using proportion of stickers won

```{r}

options(contrasts = c("contr.sum","contr.poly"))

m.stick.1 <- glm(cbind(Stickers_total, 4 - Stickers_total) ~ Condition*Age_in_years + Gender,
                 data = df_S,
                 family = binomial)

tab_model(m.stick.1, use.viewer = TRUE)

drop1(m.stick.1, test="Chisq")
drop1(update(m.stick.1, . ~ . -Condition:Age_in_years), test="Chisq")

```

##### Full model vs. Null model

```{r}

m.stick.null <- glm(cbind(Stickers_total, 4 - Stickers_total) ~ Age_in_years + Gender,
                 data = df_S,
                 family = binomial)

# test full vs. null
anova(m.stick.null, m.stick.1, test="Chisq")

```


##### Taking into account trial # in the model

###### In main text

```{r}

m.stick.t.1 <- glmer(Sticker_win ~ Condition*Age_in_years + Condition*Time +
                       (1|Participant),
                     data = df.long,
                     family = binomial,
                     control = glmerControl(optimizer = 'bobyqa', optCtrl = list(maxfun=100000)))

tab_model(m.stick.t.1, use.viewer = TRUE)

drop1(m.stick.t.1, test="Chisq")

m.stick.t.2 <- update(m.stick.t.1, . ~ . -Condition:Age_in_years -Condition:Time)
drop1(m.stick.t.2, test="Chisq")

```

###### In Supp Mat
```{r}

m.stick.t.1 <- glmer(Sticker_win ~ Condition*Age_in_years*Time +
                       (1|Participant),
                     data = df.long,
                     family = binomial,
                     control = glmerControl(optimizer = 'bobyqa', optCtrl = list(maxfun=100000)))

m.stick.t.2 <- update(m.stick.t.1, . ~ . -Condition:Age_in_years:Time)
drop1(m.stick.t.2, test="Chisq")

```

##### For each individual trial

```{r}

print("++++++++++ T1 ++++++++++")

m.stick.t1.1 <- glm(Stickers_T1_win ~ Condition*Age_in_years*Gender,
                    data = df_S,
                    family = binomial)

print("3-way interaction")
drop1(m.stick.t1.1, test="Chisq")
print("2-way interactions")
m.stick.t1.2 <- update(m.stick.t1.1, . ~ . -Condition:Age_in_years:Gender)
drop1(m.stick.t1.2, test="Chisq")

lsmeans(m.stick.t1.1, list(pairwise ~ Condition), adjust = "mvt")

print("++++++++++ T2 ++++++++++")

m.stick.t2.1 <- glm(Stickers_T2_win ~ Condition*Age_in_years*Gender,
                    data = df_S,
                    family = binomial)

print("3-way interaction")
drop1(m.stick.t2.1, test="Chisq")
print("2-way interactions")
m.stick.t2.2 <- update(m.stick.t2.1, . ~ . -Condition:Age_in_years:Gender)
drop1(m.stick.t2.2, test="Chisq")

lsmeans(m.stick.t2.1, list(pairwise ~ Condition), adjust = "mvt")

print("++++++++++ T3 ++++++++++")

m.stick.t3.1 <- glm(Stickers_T3_win ~ Condition*Age_in_years*Gender,
                    data = df_S,
                    family = binomial)

print("3-way interaction")
drop1(m.stick.t3.1, test="Chisq")
print("2-way interactions")
m.stick.t3.2 <- update(m.stick.t3.1, . ~ . -Condition:Age_in_years:Gender)
drop1(m.stick.t3.2, test="Chisq")

lsmeans(m.stick.t3.1, list(pairwise ~ Condition), adjust = "mvt")

print("++++++++++ T4 ++++++++++")

m.stick.t4.1 <- glm(Stickers_T4_win ~ Condition*Age_in_years*Gender,
                    data = df_S,
                    family = binomial)

print("3-way interaction")
drop1(m.stick.t4.1, test="Chisq")
print("2-way interactions")
m.stick.t4.2 <- update(m.stick.t4.1, . ~ . -Condition:Age_in_years:Gender)
drop1(m.stick.t4.2, test="Chisq")

lsmeans(m.stick.t4.1, list(pairwise ~ Condition), adjust = "mvt")

```

#### Number of switches

##### by cup pointed

```{r}
df_switch <- df_S %>% unite("Locations", "Stickers_T1_location", "Stickers_T2_location", "Stickers_T3_location", "Stickers_T4_location", sep=",") 
df_switch <- df_switch %>% unite("Wins", "Stickers_T1_win", "Stickers_T2_win", "Stickers_T3_win", "Stickers_T4_win", sep=",")

df_switch <- df_switch %>% dplyr::select("Participant", "Condition", contains("Locations"), contains("Wins"))

# find number of switches

list_locations <- lapply(df_switch$Locations, function(x) unlist(strsplit(x, split=","))) 
list_wins <- lapply(df_switch$Wins, function(x) unlist(strsplit(x, split=","))) 

list_responses = list_locations
for (i in 1:length(list_responses)) {
  for (j in 1:length(list_responses[[i]])) {
    if (list_wins[[i]][j] == "Y" & list_locations[[i]][j] == "L") {
      list_responses[[i]][j] <- "R"
    } else if (list_wins[[i]][j] == "Y" & list_locations[[i]][j] == "R") {
      list_responses[[i]][j] <- "L"
    } else if (list_wins[[i]][j] == "NA") {
      list_responses[[i]][j] <- "NA"
    }
  }
}

switches <- lapply(list_responses, function(x) rle(x))

df_switch$num_switches <- unlist(lapply(switches, function(x) length(x[1]$lengths) - 1))

t.test(df_switch$num_switches[which(df_switch$Condition == "Competition")], df_switch$num_switches[which(df_switch$Condition == "Cooperation")])

```

##### by correct/incorrect cup

```{r}

# find number of switches

list_switches <- lapply(df_switch$Wins, function(x) unlist(strsplit(gsub("NA","",x), split=",")))

switches <- lapply(list_switches, function(x) rle(x))

df_switch$num_switches <- unlist(lapply(switches, function(x) length(x[1]$lengths) - 1))

t.test(df_switch$num_switches[which(df_switch$Condition == "Competition")], df_switch$num_switches[which(df_switch$Condition == "Cooperation")])

summarySE(df_switch, measurevar = "num_switches", groupvars = "Condition")

```

#### Stickers by performance on other tasks (EF, memory)

```{r}

m.stick.3 <- glm(cbind(Stickers_total, 4 - Stickers_total) ~ DN_prop + S_memory_correct + Condition*Age_in_years + Gender,
                 data = df_S,
                 family = binomial)

print("main effects")
drop1(m.stick.3, test="Chisq")

tab_model(m.stick.3, use.viewer = TRUE)

```


### DV: Day-Night

```{r}
df_dn <- subset(df_S, !is.na(DN_total))

m.dn.1 <- glm(cbind(DN_total, 16 - DN_total) ~ Condition*Age_in_years + Gender,
              data = df_dn,
              family = binomial)

print("2-way interaction")
drop1(m.dn.1, test="Chisq")
print("main effects")
m.dn.2 <- update(m.dn.1, . ~ . -Condition:Age_in_years)
drop1(m.dn.2, test="Chisq")

lsmeans(m.dn.1, list(pairwise ~ Condition), adjust = "mvt")

tab_model(m.dn.1, use.viewer = TRUE)

```

### DV: Memory

```{r}

m.mem.1 <- glm(S_memory_correct ~ Condition*Age_in_years + Gender,
               data = df_S,
               family = binomial)

drop1(m.mem.1, test="Chisq")
drop1(update(m.mem.1, . ~ . -Condition:Age_in_years), test="Chisq")

lsmeans(m.mem.1, list(pairwise ~ Condition), adjust = "mvt")

tab_model(m.mem.1, use.viewer = TRUE)

```


## Figures 

### Sticker by Condition and Age

```{r, fig.width = 2}

ggplot(df_S, aes(x=Age_in_years, y = Stickers_prop, fill=Condition, color=Condition)) +
  geom_smooth(method="glm") +
  xlab('Age') +
  coord_cartesian(xlim=c(4,5), ylim=c(0,1)) +
  scale_color_manual(values=c("#84a59d", "#f6bd60"), name="Condition\n", labels=c("Competition", "Cooperation")) +
  scale_fill_manual(values=c("#84a59d", "#f6bd60"), name="Condition\n", labels=c("Competition", "Cooperation")) +
  ylab('Proportion of stickers won') +
  ggtitle('Stickers task') +
  theme_bw()

```

### Sticker over trial #

```{r, fig.width = 5, fig.height = 2}

df.long.rm <- df.long[!is.na(df.long$Sticker_win),]

# get descriptive stats for just time
df.summ.time <- with(df.long.rm, table(Sticker_win, Time))
df.summ.time.prop <- as.data.frame(prop.table(df.summ.time, c(2)))
print(subset(df.summ.time.prop, Sticker_win == "Y"))

# for time and condition

df.summ.time <- with(df.long.rm, table(Sticker_win, Condition, Time))
df.summ.time.prop <- as.data.frame(prop.table(df.summ.time, c(2,3)))

ggplot(df.summ.time.prop, aes(y=Freq, x=Condition, fill=Sticker_win)) +
  geom_bar(stat="identity") +
  facet_wrap(~Time, ncol=4) +
  scale_fill_brewer(palette="Greys", name="Sticker won\n", labels=c("No", "Yes")) +
  xlab('Proportion') + 
  theme_bw()

```


#### Continuous age

```{r, fig.width =5, fig.height = 2}
ggplot(df.long, aes(x=Age_in_years, y = as.integer(Sticker_win) - 1, fill=Condition, color=Condition)) +
  geom_smooth(method="lm") +
  facet_wrap(~Time, ncol=4) +
  xlab('Age') +
  ylab('Proportion of people') +
  coord_cartesian(xlim=c(4,5), ylim=c(0,1)) +
  scale_fill_manual(values=c("#84a59d", "#f6bd60"), name="Condition\n", labels=c("Competition", "Cooperation")) +
  scale_color_manual(values=c("#84a59d", "#f6bd60"), name="Condition\n", labels=c("Competition", "Cooperation")) +
  theme_bw() +
  theme(panel.spacing = unit(1, "lines"))
```


### Day-Night by Condition and Age

```{r, fig.width=2}

ggplot(df_S, aes(y=DN_total / 16, x = Age_in_years, fill=Condition, color=Condition)) +
  geom_smooth(method="glm") +
  coord_cartesian(xlim=c(4,5), ylim=c(0,1)) +
  xlab('Age') +
  ylab('Proportion Correct on Day-Night') +
  scale_color_manual(values=c("#84a59d", "#f6bd60"), name="Condition\n", labels=c("Competition", "Cooperation")) +
  scale_fill_manual(values=c("#84a59d", "#f6bd60"), name="Condition\n", labels=c("Competition", "Cooperation")) +
  ylab('Proportion of trials correct') +
  ggtitle('Day-Night task') +
  coord_cartesian(xlim=c(4,5), ylim=c(0,1)) +
  theme_bw()

```

### Memory by Condition and Age

```{r}

df.mem.sub <- subset(df_S, !is.na(S_memory_correct))
df.summ.mem <- with(df.mem.sub, table(S_memory_correct, Condition, Age_cat))
df.summ.mem.prop <- as.data.frame(prop.table(df.summ.mem, c(2,3)))

ggplot(df.summ.mem.prop, aes(y=Freq, x = Condition, fill=S_memory_correct)) +
  geom_bar(stat="identity") +
  facet_wrap(~Age_cat, ncol=2) +
  scale_color_brewer(palette="Greys", name="Memory question correct\n", labels=c("No", "Yes")) +
  scale_fill_brewer(palette="Greys", name="Memory question correct\n", labels=c("No", "Yes")) +
  ylab("Proportion of participants") +
  theme_bw()

df.summ.mem <- with(df.mem.sub, table(S_memory_correct, Condition))
df.summ.mem.prop <- as.data.frame(prop.table(df.summ.mem, 2))

ggplot(df.summ.mem.prop, aes(y=Freq, x = Condition, fill=S_memory_correct)) +
  geom_bar(stat="identity") +
  scale_color_brewer(palette="Greys", name="Memory question correct\n", labels=c("No", "Yes")) +
  scale_fill_brewer(palette="Greys", name="Memory question correct\n", labels=c("No", "Yes")) +
  ylab("Proportion of participants") +
  theme_bw()

```
