---
title: Stickers results for adults - Study 2b
output:
html_notebook:
code_folding: hide
highlight: tango
theme: flatly
toc: yes
toc_depth: 5
toc_float: yes
html_document:
toc: yes
toc_depth: '5'
date: '`r format(Sys.time(), "%B %d, %Y")`'
---

## Packages

Installed the necessary packages

```{r, warning=FALSE, results='hide'}
packages <- c("tidyverse", "lme4", "psych", "Rmisc", "lsmeans", "ordinal", "car", "effsize")
packages_new <- packages[!(packages %in% installed.packages()[,"Package"])]
if(length(packages_new)) install.packages(packages_new)
lapply(packages,library,character.only=T)

```

## Data import

```{r}

# find files in directory
dir_files <- list.files(getwd())

# import data
# this trimmed file only removed irrelevant columns and kept the 2nd of the 3 headers provided by Qualtrics. Nothing else was altered.
file <- dir_files[grep("Study2b_data.csv$", dir_files)]
dat_orig <- read.csv(file, na.strings = c("","-99"))

# re-label the headers
names(dat_orig) <- c("Duration.Secs", "Completion.Time", "SubjID", "Consent","Comp_Check1_1","Comp_Check1_2", "Comp_Check2_1", "Comp_Check2_2", "Comp_T1_hide", "Comp_T1_response", "Comp_T1_RT", "Comp_T2_hide", "Comp_T2_response", "Comp_T2_RT","Comp_T3_hide", "Comp_T3_response", "Comp_T3_RT","Comp_T4_hide", "Comp_T4_response", "Comp_T4_RT","Coop_Check1_1","Coop_Check1_2", "Coop_Check2_1", "Coop_Check2_2", "Coop_T1_hide", "Coop_T1_response", "Coop_T1_RT", "Coop_T2_hide", "Coop_T2_response", "Coop_T2_RT","Coop_T3_hide", "Coop_T3_response", "Coop_T3_RT","Coop_T4_hide", "Coop_T4_response", "Coop_T4_RT","Pref_game_1","Pref_person_1", "Strategy_1_1", "Strategy_2_1", "Strategy_both_1", "Feeling_task1_1", "Feeling_task2_1","Pref_person_2","Pref_game_2", "Strategy_1_2", "Strategy_2_2", "Strategy_both_2", "Feeling_task1_2", "Feeling_task2_2", "Age", "Gender","stickers_comp_you_total", "stickers_comp_them_total","stickers_coop_you_total", "stickers_coop_them_total", "first_condition", "first_preference")

# create 2 new columns: proportion wins
dat_orig$prop_comp <- dat_orig$stickers_comp_you_total / 4
dat_orig$prop_coop <- dat_orig$stickers_coop_you_total / 4
```

## Organize data

```{r}

df <- dat_orig

## merge post-task columns 

merge_names_1 <- c("Pref_game_1","Pref_person_1", "Strategy_1_1", "Strategy_2_1", "Strategy_both_1", "Feeling_task1_1", "Feeling_task2_1")
merge_names_2 <- c("Pref_game_2","Pref_person_2","Strategy_1_2", "Strategy_2_2", "Strategy_both_2", "Feeling_task1_2", "Feeling_task2_2")
merge_names <- c("Pref_game","Pref_person", "Strategy_1", "Strategy_2", "Strategy_both", "Feeling_task1", "Feeling_task2")

for (merge_n in 1:length(merge_names_1)) {
  
  # set the column names we're interested in
  m_col <- merge_names[merge_n]
  m_col1 <- merge_names_1[merge_n]
  m_col2 <- merge_names_2[merge_n]
  
  # replace NAs with empty string
  df[, m_col1] <- as.character(df[, m_col1])
  df[, m_col1][is.na(df[, m_col1])] <- ""
  df[, m_col2] <- as.character(df[, m_col2])
  df[, m_col2][is.na(df[, m_col2])] <- ""
  
  # combine column 1 and column 2
  df <- unite_(df, m_col, c(m_col1,m_col2), "")
  df[, m_col] <- as.factor(df[, m_col])
}

# remove first and second set of columns
df = df[,!(names(df) %in% c(merge_names_1, merge_names_2))]

## Exclusion: comprehension checks

# figure out which participants got the first check question for Game 1 & 2 wrong both times
# initialize variables
df$Comp_Check1.correct <- numeric(dim(df)[1])
df$Coop_Check1.correct <- numeric(dim(df)[1])
df$Comp_Check2.correct <- numeric(dim(df)[1])
df$Coop_Check2.correct <- numeric(dim(df)[1])
# if the other player guesses correctly and finds the sticker(s), who gets to keep it/them?
# comp: the other player
# coop: neither of us get to keep any stickers
df$Comp_Check1.correct[which(df$Comp_Check1_1 == 'the other player' | df$Comp_Check1_2 == 'the other player')] <- 1
df$Coop_Check1.correct[which(df$Coop_Check1_1 == 'neither of us gets to keep any stickers' | df$Coop_Check1_2 == 'neither of us gets to keep any stickers')] <- 1

# figure out which participants got the second check question for Game 1 & 2 wrong both times
# if the other player guesses incorrectly and doesn't find the sticker(s), who gets to keep it/them?
# comp: me
# coop: we each get to keep a sticker
df$Comp_Check2.correct <- numeric(dim(df)[1])
df$Comp_Check2.correct[which(df$Comp_Check2_1 == 'me' | df$Comp_Check2_2 == 'me')] <- 1
df$Coop_Check2.correct[which(df$Coop_Check2_1 == 'we each get to keep a sticker' | df$Coop_Check2_2 == 'we each get to keep a sticker')] <- 1

# create an exclude variable
df$Exclude <- 1 - (df$Comp_Check1.correct & df$Comp_Check2.correct)

# exclude participants who did not fully complete the 2 games
subjs_incomplete <- which(is.na(df$Comp_T1_hide) | is.na(df$Comp_T1_response) | is.na(df$Comp_T2_hide) | is.na(df$Comp_T2_response) | is.na(df$Comp_T3_hide) | is.na(df$Comp_T3_response) | is.na(df$Comp_T4_hide) | is.na(df$Comp_T4_response) | is.na(df$Coop_T1_hide) | is.na(df$Coop_T1_response) | is.na(df$Coop_T2_hide) | is.na(df$Coop_T2_response) | is.na(df$Coop_T3_hide) | is.na(df$Coop_T3_response) | is.na(df$Coop_T4_hide) | is.na(df$Coop_T4_response))
df$Exclude[subjs_incomplete] <- 1

# subset data by exclusion criteria
df_excl <- subset(df, Exclude == 0) %>% dplyr::select(-contains("Check"))

# turn to long format
col_hide <- which(grepl("*hide*", colnames(df_excl)))
df_long <- df_excl %>% 
  gather(key = 'question.hide', value = 'response', col_hide) %>% 
  separate(question.hide, c("condition","trial", "question"), sep = "_") %>%
  spread(question, response)

col_response <- which(grepl("*response*", colnames(df_excl)))
response <- df_excl %>% 
  gather(key = 'question.response', value = 'response', col_response) %>% 
  separate(question.response, c("condition","trial", "question"), sep = "_") %>%
  spread(question, response) %>%
  dplyr::select(response)
df_long <- cbind(df_long, response) 

col_RT <- which(grepl("*RT*", colnames(df_excl)))
RT <- df_excl %>%
  gather(key = 'timing.RT', value = 'RT', col_RT) %>% 
  separate(timing.RT, c("condition","trial", "question"), sep = "_") %>%
  spread(question, RT) %>%
  dplyr::select(RT)
df_long <- cbind(df_long, RT) %>%
  dplyr::select(-contains("_T1_"), -contains("_T2_"), -contains("_T3_"), -contains("_T4_"))

# create a new column: success
# 1 = successful; 0 = not successful
# successful if Response.to.question !=  Where.would.you.like.to.hide.the.sticker.
df_long$correct <- numeric(dim(df_long)[1])
df_long$correct[which(df_long$response != df_long$hide)] <- 1

# re-label responses to preference questions
df_long$Pref_game_cond <- NA
df_long$Pref_game_cond[which((df_long$Pref_game == "Game 1" & df_long$first_condition == "competition") | (df_long$Pref_game == "Game 2" & df_long$first_condition == "cooperation"))] <- "competition"
df_long$Pref_game_cond[which((df_long$Pref_game == "Game 1" & df_long$first_condition == "cooperation") | (df_long$Pref_game == "Game 2" & df_long$first_condition == "competition"))] <- "cooperation"
df_long$Pref_person_cond <- NA
df_long$Pref_person_cond[which((df_long$Pref_person == "Person from Game 1" & df_long$first_condition == "competition") | (df_long$Pref_person == "Person from Game 2" & df_long$first_condition == "cooperation"))] <- "Person from the competition game"
df_long$Pref_person_cond[which((df_long$Pref_person == "Person from Game 1" & df_long$first_condition == "cooperation") | (df_long$Pref_person == "Person from Game 2" & df_long$first_condition == "competition"))] <- "Person from the cooperation game"

# re-label responses to feeling questions
df_long$Feeling_comp <- factor("", c("Extremely good", "Moderately good", "Slightly good", "Neither good nor bad", "Slightly bad", "Moderately bad", "Extremely bad"))
df_long$Feeling_coop <- factor("", c("Extremely good", "Moderately good", "Slightly good", "Neither good nor bad", "Slightly bad", "Moderately bad", "Extremely bad"))
indx_comp_1st_comp <- which(df_long$first_condition == 'competition' & df_long$condition == 'Comp')
indx_comp_1st_coop <- which(df_long$first_condition == 'competition' & df_long$condition == 'Coop')
indx_coop_1st_comp <- which(df_long$first_condition == 'cooperation' & df_long$condition == 'Comp')
indx_coop_1st_coop <- which(df_long$first_condition == 'cooperation' & df_long$condition == 'Coop')
df_long$Feeling_comp[indx_comp_1st_comp] <- df_long$Feeling_task1[indx_comp_1st_comp]
df_long$Feeling_comp[indx_coop_1st_comp] <- df_long$Feeling_task2[indx_coop_1st_comp]
df_long$Feeling_coop[indx_comp_1st_coop] <- df_long$Feeling_task2[indx_comp_1st_coop]
df_long$Feeling_coop[indx_coop_1st_coop] <- df_long$Feeling_task1[indx_coop_1st_coop]
df_long <- df_long %>% 
  gather("Feeling_cond", "Feeling", c("Feeling_comp", "Feeling_coop")) %>%
  dplyr::filter(!is.na(Feeling)) %>%
  dplyr::select(-c("Feeling_cond"))

# create order variable
df_long$condition_order[which(df_long$first_condition == "competition" & df_long$condition == "Comp")] <- "first"
df_long$condition_order[which(df_long$first_condition == "competition" & df_long$condition == "Coop")] <- "second"
df_long$condition_order[which(df_long$first_condition == "cooperation" & df_long$condition == "Coop")] <- "first"
df_long$condition_order[which(df_long$first_condition == "cooperation" & df_long$condition == "Comp")] <- "second"

# convert to proper class
df_long$trial <- ordered(as.factor(df_long$trial))
df_long$condition <- as.factor(df_long$condition)
df_long$hide <- as.factor(df_long$hide)
df_long$response <- as.factor(df_long$response)
df_long$condition_order <- as.factor(df_long$condition_order)
df_long$Feeling_task1 <- ordered(df_long$Feeling_task1, levels = c("Extremely good", "Moderately good", "Slightly good", "Neither good nor bad", "Slightly bad", "Moderately bad", "Extremely bad"))
df_long$Feeling_task2 <- ordered(df_long$Feeling_task2, levels = c("Extremely good", "Moderately good", "Slightly good", "Neither good nor bad", "Slightly bad", "Moderately bad", "Extremely bad"))
df_long$Feeling <- ordered(df_long$Feeling, levels = c("Extremely good", "Moderately good", "Slightly good", "Neither good nor bad", "Slightly bad", "Moderately bad", "Extremely bad"))
df_long$Feeling_score <- as.integer(df_long$Feeling)
df_long$Pref_game_cond <- as.factor(df_long$Pref_game_cond)
df_long$Pref_person_cond <- as.factor(df_long$Pref_person_cond)
df_long <- droplevels(df_long)

```

## Descriptive stats

Number of people excluded

```{r}

print("number of exclusions")
dim(dat_orig)[1] - dim(df_excl)[1]

print("Demographics for people who completed the survey")
mean(dat_orig$Age, na.rm=TRUE)
sd(dat_orig$Age, na.rm=TRUE)
summary(dat_orig[,c("Age", "Gender")])

```

Number of people left after exclusion criteria

```{r}

dim(df_excl)[1]

print("Demographics for people who passed comp checks")
mean(df_excl$Age, na.rm=TRUE)
sd(df_excl$Age, na.rm=TRUE)
summary(df_excl[,c("Age", "Gender")])

```

### Effect size calculation

Proportion of stickers won for cooperation vs. competition

```{r}

v_props <- c(df_excl$prop_comp, df_excl$prop_coop)
v_groups <- as.factor(cbind(rep("competition", length(df_excl$prop_comp)),rep("cooperation", length(df_excl$prop_coop))))
df_eff <- data.frame(v_props, v_groups)
effsize::cohen.d(df_eff$v_props, relevel(df_eff$v_groups, ref="cooperation"))

```


## Excluded people who failed comp checks

### Figures

#### Proportions

```{r, fig.height = 1, fig.width = 2}

dat_summ <- summarySE(df_long, measurevar="correct", groupvars = c("condition"))
ggplot(dat_summ, aes(y=correct, x=condition, fill=condition)) +
  geom_bar(stat="identity", position=position_dodge(), width = 0.5) +
  geom_errorbar(aes(ymin=correct-ci, ymax=correct+ci, width=.2)) +
  coord_cartesian(y=c(0,1)) +
  ylab("Proportion of trials won") +
  xlab("Condition") +
  ggtitle("Study 2b") +
  scale_x_discrete(labels=c("Coop" = "Cooperation", "Comp" = "Competition")) +
  scale_fill_manual(values=c("#84a59d", "#f6bd60"), name="Condition\n", labels=c("Competition", "Cooperation")) +
  theme_bw()
```

#### Proportions by order of task presentation

```{r, fig.width=3, fig.height=2}
ggplot(df_long, aes(y = correct, x = condition, color = condition)) +
  stat_summary(fun.data = "mean_cl_boot") +
  facet_wrap(~condition_order, ncol=2) +
  scale_color_manual(values=c("#84a59d", "#f6bd60"), name="Condition\n", labels=c("Competition", "Cooperation")) +
  scale_x_discrete(labels=c("Coop" = "cooperation", "Comp" = "competition")) +
  coord_cartesian(y=c(0,1)) +
  theme_bw()
```


#### Preferences

```{r, fig.width = 3, fig.height=1.5}

df_pref <- df_long %>% gather("Pref_question", "Pref_response", c("Pref_game_cond", "Pref_person_cond"))
df_pref <- as.data.frame(table(df_pref[,c("Pref_response", "Pref_question")]) / 8)
names(df_pref) <- c("Response", "Question","Freq")
df_pref$Prop <- df_pref$Freq / (sum(df_pref$Freq) / 2)
df_pref <- df_pref %>% dplyr::filter(Prop > 0)

ggplot(df_pref, aes(y=Prop, x = Question, fill=Response)) +
  geom_bar(stat="identity", width=0.8) +
  scale_fill_manual(values=c("#84a59d", "#f6bd60", "#84a59d", "#f6bd60")) +
  geom_text(aes(label=Response), position=position_stack(vjust = .5), color="white", size=2.5) +
  ylab("Proportion of participants") +
  xlab(NULL) +
  scale_x_discrete(labels=c("Pref_game_cond" = "Which game would you\nrather play again?", "Pref_person_cond" = "Which person would you\nrather play a different game with?")) +
  theme_bw() +
  theme(
    legend.position = "none")

```

#### Feelings

```{r, fig.width=2.5, fig.height=2}
tb_feeling <- table(df_long$Feeling, df_long$condition) / 4
df_feeling <- as.data.frame(tb_feeling)
names(df_feeling) <- c("rating", "condition", "freq")
df_feeling$rating <- ordered(df_feeling$rating, levels = c("Extremely good", "Moderately good", "Slightly good", "Neither good nor bad", "Slightly bad", "Moderately bad", "Extremely bad"))

ggplot(df_feeling, aes(y=freq, x=rating, fill=condition)) +
  geom_bar(stat="identity") +
  facet_wrap(~condition, ncol=1, labeller=as_labeller(c(Coop = "Cooperation", Comp = "Competition"))) +
  scale_fill_manual(values=c("#84a59d", "#f6bd60")) +
  ylab("Frequency") +
  xlab("How did you feel about clicking on the empty cup\nwhen responding to the other player's question?") +
  theme_bw() +
  theme(legend.position = "none",
        axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0)),
        axis.text.x = element_text(angle = 30, hjust=1))
```

### Analyses

#### Binary: correct/incorrect

```{r}

model1 = glmer(as.factor(correct) ~ condition*Age + Gender + condition_order +
                 (1 | SubjID) + (1|trial),
               data = df_long,
               family = binomial,
               control = glmerControl(optimizer = 'bobyqa', optCtrl = list(maxfun=100000)))

drop1(model1, test="Chisq")

model1.1 <- update(model1, . ~ . -condition:Age)
drop1(model1.1, test="Chisq")

lsmeans(model1.1, list(pairwise ~ condition_order), adjust = "mvt")

```

##### Comparing to null model

```{r}

model1.null = glmer(as.factor(correct) ~ Age + Gender + condition_order +
                 (1 | SubjID) + (1|trial),
               data = df_long,
               family = binomial,
               control = glmerControl(optimizer = 'bobyqa', optCtrl = list(maxfun=100000)))

anova(model1, model1.null, test="Chisq")
```

#### Binary: correct/incorrect with trial as predictor

```{r}

model1 = glmer(as.factor(correct) ~ condition*trial + (1|SubjID),
               data = df_long,
               family = binomial,
               control = glmerControl(optimizer = 'bobyqa', optCtrl = list(maxfun=100000)))

drop1(model1, test="Chisq")

drop1(update(model1, . ~ . -condition:trial), test="Chisq")

```

#### T1: correct/incorrect

```{r}

df.t1 <- subset(df_long, trial == "T1")

model1 = glm(as.factor(correct) ~ condition*Age + Gender + condition_order,
               data = df.t1,
               family = binomial)

drop1(model1, test="Chisq")

model1.1 <- update(model1, . ~ . -condition:Age)
drop1(model1.1, test="Chisq")

```
#### T2: correct/incorrect

```{r}

df.t2 <- subset(df_long, trial == "T2")

model1 = glm(as.factor(correct) ~ condition*Age + Gender + condition_order,
               data = df.t2,
               family = binomial)

drop1(model1, test="Chisq")

model1.1 <- update(model1, . ~ . -condition:Age)
drop1(model1.1, test="Chisq")

```

#### T3: correct/incorrect

```{r}

df.t3 <- subset(df_long, trial == "T3")

model1 = glm(as.factor(correct) ~ condition*Age + Gender + condition_order,
               data = df.t3,
               family = binomial)

drop1(model1, test="Chisq")

model1.1 <- update(model1, . ~ . -condition:Age)
drop1(model1.1, test="Chisq")

```

#### T4: correct/incorrect

```{r}

df.t4 <- subset(df_long, trial == "T4")

model1 = glm(as.factor(correct) ~ condition*Age + Gender + condition_order,
               data = df.t4,
               family = binomial)

drop1(model1, test="Chisq")

model1.1 <- update(model1, . ~ . -condition:Age)
drop1(model1.1, test="Chisq")
```

#### Number of switches per person

```{r}

df_switch <- df_excl %>% unite("Comp_Responses", "Comp_T1_response", "Comp_T2_response", "Comp_T3_response", "Comp_T4_response", sep=",") %>% dplyr::select("SubjID", "Comp_Responses", "first_condition", contains("_response"))
df_switch <- df_switch %>% unite("Coop_Responses", "Coop_T1_response", "Coop_T2_response", "Coop_T3_response", "Coop_T4_response", sep=",")

# find number of switches

list_switches_comp <- lapply(df_switch$Comp_Responses, function(x) unlist(strsplit(x, split=","))) 
list_switches_coop <- lapply(df_switch$Coop_Responses, function(x) unlist(strsplit(x, split=",")))

switches_comp <- lapply(list_switches_comp, function(x) rle(x))
switches_coop <- lapply(list_switches_coop, function(x) rle(x))

df_switch$num_switches_comp <- unlist(lapply(switches_comp, function(x) length(x[1]$lengths) - 1))
df_switch$num_switches_coop <- unlist(lapply(switches_coop, function(x) length(x[1]$lengths) - 1))

df_switch <- df_switch %>% gather("condition", "num_switches", c("num_switches_comp", "num_switches_coop"))
df_switch <- df_switch %>% separate(condition, c("num","switches","condition")) %>% dplyr::select(-c("num", "switches"))

df_switch$condition_order <- NA
df_switch$condition_order[which(df_switch$first_condition == "competition" & df_switch$condition == "comp")] <- "first"
df_switch$condition_order[which(df_switch$first_condition == "cooperation" & df_switch$condition == "coop")] <- "first"
df_switch$condition_order[which(df_switch$first_condition == "competition" & df_switch$condition == "coop")] <- "second"
df_switch$condition_order[which(df_switch$first_condition == "cooperation" & df_switch$condition == "comp")] <- "second"

print("----- total -----")
t.test(df_switch$num_switches[which(df_switch$condition == "comp")],
       df_switch$num_switches[which(df_switch$condition == "coop")])
print("----- first presented variant -----")
t.test(df_switch$num_switches[which(df_switch$condition_order == "first" & df_switch$condition == "comp")],
       df_switch$num_switches[which(df_switch$condition_order == "first" & df_switch$condition == "coop")])
print("----- second presented variant -----")
t.test(df_switch$num_switches[which(df_switch$condition_order == "second" & df_switch$condition == "comp")],
       df_switch$num_switches[which(df_switch$condition_order == "second" & df_switch$condition == "coop")])

```

#### RT

```{r}

model2 = lmer(RT ~ condition*Age + Gender + condition_order +
                (1 | SubjID) + (1|trial),
              data = df_long)

drop1(model2, test="Chisq")


model2.1 <- update(model2, . ~ . -condition:Age)
drop1(model2.1, test="Chisq")


```

#### Preference: Game

```{r}

tb_game <- table(df_long[,c("Pref_game_cond")]) / 8
tb_game

chisq.test(tb_game)

```

#### Preference: Person

```{r}

tb_person <- table(df_long[,c("Pref_person_cond")]) / 8
tb_person
chisq.test(tb_person)

```

#### Feelings

```{r, width=10, height=1}

df_feeling <- df_long %>% group_by(SubjID, condition) %>% dplyr::summarise(Feeling_score = mean(Feeling_score))
wilcox.test(Feeling_score ~ condition, data = df_feeling, paired=TRUE)

```

#### Model with other factors

```{r}

model1 = glm(as.factor(correct) ~ condition + Age + Gender + condition_order + Feeling + Pref_game_cond + Pref_person_cond + RT + trial,
               data = df_long,
               family = binomial)

drop1(model1, test="Chisq")

```
