---
title: Stickers results for adults - Study 2a
output:
  html_notebook:
    code_folding: hide
    highlight: tango
    theme: flatly
    toc: yes
    toc_depth: 5
    toc_float: yes
  html_document:
    toc: yes
    toc_depth: '5'
date: '`r format(Sys.time(), "%B %d, %Y")`'
---

## Packages

Installed the necessary packages

```{r, warning=FALSE, results='hide'}
packages <- c("tidyverse", "lme4", "psych", "Hmisc", "lsmeans", "Rmisc")
packages_new <- packages[!(packages %in% installed.packages()[,"Package"])]
if(length(packages_new)) install.packages(packages_new)
lapply(packages,library,character.only=T)

```

## Data import

```{r}

# find files in directory
dir_files <- list.files(getwd())

# import data
file <- dir_files[grep("Study2a_data.csv$", dir_files)]
dat_orig <- read.csv(file, na.strings = c("","-99"))

```

## Organize data

```{r}
# exclude participants who get the question on the instruction page wrong
# comp: the other player
# coop: neither of us gets to keep any stickers
dat_orig$rule.correct <- numeric(dim(dat_orig)[1])
dat_orig$rule.correct[which(dat_orig$condition == 'competition' & dat_orig$Rule == 'the other player')] <- 1
dat_orig$rule.correct[which(dat_orig$condition == 'cooperation' & dat_orig$Rule == 'neither of us gets to keep any stickers')] <- 1

# exclude participants for those who get comp questions wrong

# if the other player guesses correctly and finds the stickers, who gets to keep them?
# comp: the other player
# coop: neither of us gets to keep any stickers
dat_orig$comp1 <- numeric(dim(dat_orig)[1])
dat_orig$comp1[which(dat_orig$condition == 'competition' &
                       dat_orig$If.the.other.player.guesses.correctly.and.finds.the.stickers..who.gets.to.keep.them. == 'the other player')] <- 1
dat_orig$comp1[which(dat_orig$condition == 'cooperation' &
                       dat_orig$If.the.other.player.guesses.correctly.and.finds.the.stickers..who.gets.to.keep.them. == 'neither of us gets to keep any stickers')] <- 1

# if the other player guesses incorrectly and doesn't find the stickers, who gets to keep them?
# comp: me
# coop-4: we each get to keep a sticker
# coop-8: we each get to keep a sheet of stickers
dat_orig$comp2 <- numeric(dim(dat_orig)[1])
dat_orig$comp2[which(dat_orig$condition == 'competition' & dat_orig$If.the.other.player.guesses.incorrectly.and.doesn.t.find.the.stickers..who.gets.to.keep.them. == 'me')] <- 1
dat_orig$comp2[which(dat_orig$condition == 'cooperation' & dat_orig$stickers_num == 4 &
                       dat_orig$If.the.other.player.guesses.incorrectly.and.doesn.t.find.the.stickers..who.gets.to.keep.them. == 'we each get to keep a sticker')] <- 1
dat_orig$comp2[which(dat_orig$condition == 'cooperation' & dat_orig$stickers_num == 8 &
                       dat_orig$If.the.other.player.guesses.incorrectly.and.doesn.t.find.the.stickers..who.gets.to.keep.them. == 'we each get to keep a sheet of stickers')] <- 1

# exclude participants who only partially filled out survey
dat_completed <- subset(dat_orig, !is.na(Trial.1_Hide) & !is.na(Trial.1_Response) & !is.na(Trial.2_Hide) & !is.na(Trial.2_Response) & !is.na(Trial.3_Hide) & !is.na(Trial.3_Response) & !is.na(Trial.4_Hide) & !is.na(Trial.4_Response))

dat_removed <- subset(dat_completed, comp1 == 1 & comp2 == 1 & rule.correct == 1)

# turn to long format
col_hide <- which(grepl("Trial.*", colnames(dat_removed)))
dat_rem_long <- dat_removed %>% 
  gather(key = 'question.hide', value = 'response', col_hide) %>% 
  separate(question.hide, c("trial", "question"), sep = "_") %>%
  spread(question, response)

# create a new column: success
# 1 = successful; 0 = not successful
# successful if Response.to.question !=  Where.would.you.like.to.hide.the.sticker.
dat_rem_long$correct <- numeric(dim(dat_rem_long)[1])
dat_rem_long$correct[which(dat_rem_long$Response != dat_rem_long$Hide)] <- 1

# convert to proper class
dat_rem_long$SubjID <- as.factor(dat_rem_long$SubjID)
dat_rem_long$trial <- ordered(as.factor(dat_rem_long$trial))

# turn to wide format

# create a column with just the proportion
dat_rem_prop <- dat_rem_long %>% 
  group_by(SubjID, condition, stickers_num, stickers_you_total, Age, Gender) %>%
  dplyr::summarise(mean = mean(correct))

dat_all <- dat_orig

# turn to long format
columns <- which(grepl("Trial.*", colnames(dat_all)))
dat_all_long <- dat_all %>% 
  gather(key = 'trial', value = 'response', columns) %>%
  separate(trial, c("trial", "question"), sep = "_") %>%
  spread(question, response)

# create a new column: success
# 1 = successful; 0 = not successful
# successful if Response.to.question !=  Where.would.you.like.to.hide.the.sticker.
dat_all_long$correct <- numeric(dim(dat_all_long)[1])
dat_all_long$correct[which(dat_all_long$Response != dat_all_long$Hide)] <- 1

# convert to proper class
dat_all_long$SubjID <- as.factor(dat_all_long$SubjID)
dat_all_long$trial <- ordered(as.factor(dat_all_long$trial))

# turn to wide format

# create a column with just the proportion
dat_all_prop <- dat_all_long %>% 
  group_by(SubjID, condition, stickers_num) %>%
  dplyr::summarise(mean = mean(correct))

```

## Tables: counts

### Number of people who completed the task
```{r}

with(dat_completed, table(condition, stickers_num))
```

### Number of people who passed question on instruction page and comp checks afterward

```{r}

with(subset(dat_rem_long, trial=="Trial.1"), table(condition, stickers_num))

```

### Number of people who mentioned deception

```{r}

print("No")

tb_decep <- with(subset(dat_rem_long, trial=="Trial.1" & coded_response == "N"), table(condition))

tb_decep

chisq.test(tb_decep)

print("Yes")

tb_decep <- with(subset(dat_rem_long, trial=="Trial.1" & coded_response == "Y"), table(condition))

tb_decep

chisq.test(tb_decep)

```


## Excluded people who failed comp checks

### Descriptive stats

Demographics

```{r}

print("Demographics for people who completed the survey")
summary(dat_completed[,c("Age", "Gender")])
print("Demographics for people who passed comp checks")
summary(dat_rem_prop)

```

### Effect size calculation

Proportion of stickers won for cooperation vs. competition

```{r}

cohen.d(dat_rem_prop$mean, relevel(dat_rem_prop$condition, ref="cooperation"))

```


Grouped by trial #

```{r, fig.height=2, fig.width=5}

dat_rem_trial <- summarySE(dat_rem_long, measurevar="correct", groupvars = c("trial", "condition"))

ggplot(dat_rem_trial, aes(x=condition, y=correct, fill=condition)) +
  geom_bar(stat="identity", position = position_dodge()) +
  geom_errorbar(aes(ymin=correct-ci, ymax=correct+ci), width=0.2) +
  facet_wrap(~trial, ncol=4) +
  coord_cartesian(y=c(0,1)) +
  xlab("Condition") +
  ylab("Proportion of people winning the sticker") +
  scale_color_manual(values=c("#84a59d", "#f6bd60"), name="Condition\n", labels=c("Competition", "Cooperation")) +
  scale_fill_manual(values=c("#84a59d", "#f6bd60"), name="Condition\n", labels=c("Competition", "Cooperation")) +
  theme_bw()

```


### Figures

#### By condition

```{r, fig.height = 1, fig.width = 2}
ggplot(dat_rem_prop, aes(y = mean, x = condition)) +
  stat_summary(fun.data = "mean_cl_boot") +
  coord_cartesian(y=c(0,1)) +
  scale_color_manual(values=c("#84a59d", "#f6bd60"), name="Condition\n", labels=c("Competition", "Cooperation")) +
  scale_fill_manual(values=c("#84a59d", "#f6bd60"), name="Condition\n", labels=c("Competition", "Cooperation")) +
  theme_classic()

ggplot(dat_rem_prop, aes(y = mean, x = condition)) +
  stat_summary(fun.data = "mean_cl_boot") +
  facet_wrap(~stickers_num, ncol=2) +
  scale_color_manual(values=c("#84a59d", "#f6bd60"), name="Condition\n", labels=c("Competition", "Cooperation")) +
  scale_fill_manual(values=c("#84a59d", "#f6bd60"), name="Condition\n", labels=c("Competition", "Cooperation")) + 
  coord_cartesian(y=c(0,1)) +
  theme_classic()

dat_summ <- summarySE(dat_rem_long, measurevar="correct", groupvars = c("condition"))
ggplot(dat_summ, aes(y=correct, x=condition, fill=condition)) +
  geom_bar(stat="identity", position=position_dodge(), width = 0.5) +
  geom_errorbar(aes(ymin=correct-ci, ymax=correct+ci, width=.2)) +
  coord_cartesian(y=c(0,1)) +
  ylab("Proportion of trials won") +
  xlab("Condition") +
  ggtitle("Study 2a") +
  scale_x_discrete(labels=c("Coop" = "Cooperation", "Comp" = "Competition")) +
  scale_fill_manual(values=c("#84a59d", "#f6bd60"), name="Condition\n", labels=c("Competition", "Cooperation")) +
  theme_bw()

print(dat_summ)
```


### Analyses

Analysis with proportion data

```{r}

model.p.1 = glm(cbind(stickers_you_total, stickers_num - stickers_you_total) ~ condition*Age + as.factor(stickers_num) + Gender,
              data = dat_rem_prop,
              family = binomial)

drop1(model.p.1, test="Chisq")

model.p.2 <- update(model.p.1, . ~ . -condition:Age)
drop1(model.p.2, test="Chisq")

```

#### Comparison with null model

```{r}

model.p.1.null = glm(cbind(stickers_you_total, stickers_num - stickers_you_total) ~ as.factor(stickers_num) + Age + Gender,
              data = dat_rem_prop,
              family = binomial)

anova(model.p.1.null, model.p.1, test="Chisq")

```

##### Analysis with binary response term

```{r}

model.b.1 = glmer(as.factor(correct) ~ condition*Age + Gender + as.factor(stickers_num) +
                (1 | SubjID) + (1|trial),
              data = dat_rem_long,
              family = binomial,
              control = glmerControl(optimizer = 'bobyqa', optCtrl = list(maxfun=100000)))

drop1(model.b.1, test="Chisq")

model.b.2 = update(model.b.1, . ~ . -condition:Age)
drop1(model.b.2, test="Chisq")

```

##### With trial as a predictor

```{r}

model.b.t.1 <- glmer(as.factor(correct) ~ condition*trial +
                (1 | SubjID),
              data = dat_rem_long,
              family = binomial,
              control = glmerControl(optimizer = 'bobyqa', optCtrl = list(maxfun=100000)))

drop1(model.b.t.1, test="Chisq")

drop1(update(model.b.t.1, . ~ . -condition:trial), test="Chisq")

dat_trial_summ <- summarySE(dat_rem_long, measurevar="correct", groupvars = c("trial"))

print(dat_trial_summ)

```

##### Analysis for each trial

Trial 1

```{r}

dat_t1 <- subset(dat_rem_long, trial == "Trial.1")
m.stick.t.1 <- glm(as.factor(correct) ~ + condition*Age + Gender + as.factor(stickers_num),
                     data = dat_t1,
                     family = binomial)

drop1(m.stick.t.1, test="Chisq")

m.stick.t.1.1 <- update(m.stick.t.1, . ~ . -condition:Age)
drop1(m.stick.t.1.1, test="Chisq")

```

Trial 2

```{r}

dat_t2 <- subset(dat_rem_long, trial == "Trial.2")
m.stick.t.2 <- glm(as.factor(correct) ~ + condition*Age + Gender + as.factor(stickers_num),
                     data = dat_t2,
                     family = binomial)

drop1(m.stick.t.2, test="Chisq")

m.stick.t.2.1 <- update(m.stick.t.2, . ~ . -condition:Age)
drop1(m.stick.t.2.1, test="Chisq")

```

Trial 3

```{r}

dat_t3 <- subset(dat_rem_long, trial == "Trial.3")
m.stick.t.3 <- glm(as.factor(correct) ~ + condition*Age + Gender + as.factor(stickers_num),
                     data = dat_t3,
                     family = binomial)

drop1(m.stick.t.3, test="Chisq")

m.stick.t.3.1 <- update(m.stick.t.3, . ~ . -condition:Age)
drop1(m.stick.t.3.1, test="Chisq")

```

Trial 4

```{r}

dat_t4 <- subset(dat_rem_long, trial == "Trial.4")
m.stick.t.4 <- glm(as.factor(correct) ~ + condition*Age + Gender + as.factor(stickers_num),
                     data = dat_t4,
                     family = binomial)

drop1(m.stick.t.4, test="Chisq")

m.stick.t.4.1 <- update(m.stick.t.4, . ~ . -condition:Age)
drop1(m.stick.t.4.1, test="Chisq")

```

#### Number of switches per person

##### by pointed cup

```{r, fig.width =2}

df_switch <- dat_removed %>% unite("Responses", "Trial.1_Response", "Trial.2_Response", "Trial.3_Response", "Trial.4_Response", sep=",") %>% dplyr::select("SubjID", "Responses", "condition", contains("Responses"))

# find number of switches

list_switches <- lapply(df_switch$Responses, function(x) unlist(strsplit(x, split=","))) 

switches <- lapply(list_switches, function(x) rle(x))

df_switch$num_switches <- unlist(lapply(switches, function(x) length(x[1]$lengths) - 1))

t.test(df_switch$num_switches[which(df_switch$condition == "competition")], df_switch$num_switches[which(df_switch$condition == "cooperation")])

```

##### by incorrect/correct cup

```{r}

df_switch <- dat_removed %>% unite("Responses", "Trial.1_Response", "Trial.2_Response", "Trial.3_Response", "Trial.4_Response", sep=",") %>% dplyr::select("SubjID", "Responses", "condition", contains("Responses"))
df_switch_hide <- dat_removed %>% unite("Hides", "Trial.1_Hide", "Trial.2_Hide", "Trial.3_Hide", "Trial.4_Hide", sep=",") %>% dplyr::select("SubjID", "Hides", "condition", contains("Hides"))
df_switch <- left_join(df_switch, df_switch_hide, by=c("SubjID","condition"))

count_switches <- function(v_hide, v_response) {
  var_return <- ""
  for (t in seq(1,8,2)) {
    if (((substring(v_hide,t,t) == '1') & (substring(v_response,t,t) == '1')) | ((substring(v_hide,t,t) == '2') & (substring(v_response,t,t) == '2'))) {
      var_return <- paste(var_return, "I", sep=",")
    } else {
      var_return <- paste(var_return, "C", sep=",")
    }
  }
  return(substring(var_return, 2))
}

df_switch$Switches_Correct <- mapply(count_switches, v_hide=df_switch$Hides, v_response=df_switch$Responses)

# find number of switches

list_switches <- lapply(df_switch$Switches_Correct, function(x) unlist(strsplit(x, split=","))) 

switches <- lapply(list_switches, function(x) rle(x))

df_switch$num_switches <- unlist(lapply(switches, function(x) length(x[1]$lengths) - 1))

t.test(df_switch$num_switches[which(df_switch$condition == "competition")], df_switch$num_switches[which(df_switch$condition == "cooperation")])

summarySE(df_switch, measurevar = "num_switches", groupvars = "condition")

```

## Including all people


### Figures

```{r}
ggplot(dat_all_prop, aes(y = mean, x = condition)) +
  stat_summary(fun.data = "mean_cl_boot") +
  coord_cartesian(y=c(0,1)) +
  theme_classic()

ggplot(dat_all_prop, aes(y = mean, x = condition)) +
  stat_summary(fun.data = "mean_cl_boot") +
  facet_wrap(~stickers_num, ncol=2) +
  coord_cartesian(y=c(0,1)) +
  theme_classic()

```


### Analyses

```{r}

model2 = glmer(correct ~ condition +
                (1 | SubjID) + (1|trial),
              data = dat_all_long,
              family = binomial)

drop1(model2, test="Chisq")

```

With trial as a predictor

```{r}

model2 = glmer(correct ~ condition*trial +
                (1 | SubjID),
              data = dat_all_long,
              family = binomial)

drop1(model2, test="Chisq")

model3 = update(model2, . ~ . -condition:trial)
drop1(model3, test="Chisq")

```


